\vspace*{-5mm}
\mysection{Overall Description}

\mysubsection{Goals \& Requirements}
\vspace{0.2cm}
\mysubsubsection{EasyLib}
\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{1}$] : Allow the user to register and login into the system (also throughout external services)}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The system has to check the credentials.
	\item \lbrack R$_{2}$] : A registered user must be able to log in the system.
	\item \lbrack R$_{3}$] : The System has to handle the connection and user requests.
	\item \lbrack R$_{4}$] : The system has to be able to save locally the user credentials to allow the automatic login.
	\item \lbrack R$_{5}$] : The system has to be able to communicate with the external services and receive the responses.
	\item \lbrack R$_{6}$] : The system has to be able to show to the user his profile information.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{2}$] : Allow the user to select his favourite library}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The system has to be able to check and retrieve libraries information from the DB.
	\item \lbrack R$_{2}$] : The system has to be able to recognize the libraries already set as favourite by the user.
	\item \lbrack R$_{3}$] : The system has to be able to set the preferred library selected by the user into the DB.
	\item \lbrack R$_{4}$] : The system has to be able to remove a library from the favourite libraries present in DB for the considered user.
	\item \lbrack R$_{5}$] : The system has to be able to show to the user his favourite libraries.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{3}$] : Allow the user to see all the libraries available into the system and their content}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The system has to be able to retrieve library’s information and contents.
	\item \lbrack R$_{2}$] : The system has to be able to show the retrieved information and contents related to the libraries.
\end{itemize}

\newpage
\noindent
\emph{\textbf{[G$_{4}$] : Allow the user to search a book in the available libraries}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The system has to be able to retrieve book’s information from the libraries using	title, author, genre and/or library name.
	\item \lbrack R$_{2}$] : The system has to be able to filter books using the book identifier, so it will show only one copy of the book even if it's present in more than one library.
	\item \lbrack R$_{3}$] : The system has to be able to show the book information to the user.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{5}$] : Allow user to retrieve book information through QRcode scan}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The android app needs to have access to the camera sensor.
	\item \lbrack R$_{2}$] : The android app has to be able to decode the QRcode attached to the book.
	\item \lbrack R$_{3}$] : The system has to be able to retrieve book information using the identifier decoded.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{6}$] : Allow the user to receive notifications from the server}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The Application Server has to be able to send notifications to the android app.
	\item \lbrack R$_{2}$] : The Android app as to be able to receive and handle incoming notifications.
	\item \lbrack R$_{3}$] : The Android app has to be able to show the notifications to the user.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{7}$] : Allow the user to reserve books}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The System has to retrieve the information of the book status from the DB.
	\item \lbrack R$_{2}$] : The System has to be able to change the status of the book to reserved / not reserved.
	\item \lbrack R$_{3}$] : The System has to show to the user all the books that he reserved.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{8}$] : Allow the user to get in line for a book}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The System has to retrieve the information of the book status from the DB.
	\item \lbrack R$_{2}$] : The System has to be able to change the status of the book to “on waiting list” / “not in waiting list”.
	\item \lbrack R$_{3}$] : The System has to show to the user all the books for which he is in line.
	\item \lbrack R$_{4}$] : The System has to be able to manage the waiting list flowing when some reservation related to the considered book is removed.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{9}$] : Allow the user to see the books that he read}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The System has to be able to retrieve the books read from the user.
	\item \lbrack R$_{2}$] : The Android application has to be able to show the books read by the user.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{10}$] : Allow the user to rate a read book}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The System has to be able to retrieve the books’ information.
	\item \lbrack R$_{2}$] : The System has to be able to recognize if the book has been read by the user.
	\item \lbrack R$_{3}$] : The System has to be able to insert the user rating into the DB.
	\item \lbrack R$_{4}$] : The DB has to be able to update the average rating after each rate insertion.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{11}$] : Allow the user to reserve a seat for an event}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The System has to be able to retrieve the events from the DB.
	\item \lbrack R$_{2}$] : The System has to check the available seats.
	\item \lbrack R$_{3}$] : The System has to allow the user to insert his participation to the event in the DB.
	\item \lbrack R$_{4}$] : The System has to allow the user to remove his participation to the event in the DB.
	\item \lbrack R$_{5}$] : The Android application has to show to the user his status related to the participation to an event.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{12}$] : Allow the user to see all the events that he joined}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The System has to be able to retrieve all the events joined by the considered user.
	\item \lbrack R$_{2}$] : The Android application has to be able to show the events joined by the user.
\end{itemize}

\newpage
\noindent
\emph{\textbf{[G$_{13}$] : Allow the user to edit his profile information}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The Android application has to be able to show to the user his profile information.
	\item \lbrack R$_{2}$] : The System has to be able to retrieve the user’s profile information from the DB.
	\item \lbrack R$_{3}$] : The System has to be able to update user’s profile information into the DB.
\end{itemize}

\vspace{0.8cm}
\mysubsubsection{EasyLib - Librarian}
\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{1}$] : Allow the librarian to login into the system}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The system has to check the credentials.
	\item \lbrack R$_{2}$] : Registered user must be able to log in the system.
	\item \lbrack R$_{3}$] : The system has to handle the connection and user requests.
	\item \lbrack R$_{4}$] : The system has to be able to show to the user his relative library information.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{2}$] : Allow librarian to retrieve book information through QRcode scan}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The android app needs to have access to the camera sensor.
	\item \lbrack R$_{2}$] : The android app has to be able to decode the QRcode attached to the book.
	\item \lbrack R$_{3}$] : The system has to be able to retrieve the book information using the identifier decoded.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{3}$] : Allow the librarian to confirm/remove reservations for a specific book}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The system has to be able to retrieve the reservation list for a book.
	\item \lbrack R$_{2}$] : The system has to be able to get the librarian input and change the reservation status of a book.
\end{itemize}

\vspace{0.5cm}
\noindent
\emph{\textbf{[G$_{3}$] : Allow the librarian to communicate to the system when a book is returned}}
\begin{itemize}
	\setlength{\leftskip}{0.5cm}
	\item \lbrack R$_{1}$] : The system has to be able to retrieve book information and check its status.
	\item \lbrack R$_{2}$] : The system has to be able to trigger the insert in the reservation list of the requests in waiting list and send them a notification.
\end{itemize}

\mysubsubsection{EasyLib - Librarian (Future Work)}
\vspace{0.5cm}
\noindent
\emph{\textbf{[FW$_{1}$] : Allow the librarian to register into the system.}}

\vspace{0.5cm}
\noindent
\emph{\textbf{[FW$_{2}$] : The system has to be able to save locally the librarian credentials to allow the automatic login.}}

\vspace{0.5cm}
\noindent
\emph{\textbf{[FW$_{3}$] : Allow the librarian to search for a book in his library.}}

\vspace{0.5cm}
\noindent
\emph{\textbf{[FW$_{4}$] : Allow the librarian to edit library information.}}

\vspace{0.5cm}
\noindent
\emph{\textbf{[FW$_{5}$] : Allow the librarian to change library contents (add/remove news, events and books).}}






\mysubsection{Product Functions}


\mysubsection{Domanin Properties}